---
title: "Drakes Creek Scramble Information"
author: "Luke Garnett"
date: "Updated:`r Sys.time()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth:  4
    css: style.css
---

```{r include=FALSE}
require(knitr)
require(mosaic)
require(DT)
require(kableExtra)
library(xtable)
library(readxl)
library(rJava)
library(xlsx)
library(googlesheets4)
library(ggplot2)
```

## Splits

Men's 3rd and 4th lap split is an estimate based on the time from mile 2 to mile 4. Women's 3 mile and final 0.11 are also estimates, but should be more accurate than the men.

```{r echo=FALSE, results='asis'}
data <- read.xlsx2("meetsplits.xlsx",sheetIndex=1,colClasses=c("character","POSIXct","POSIXct","POSIXct","POSIXct","POSIXct"))
data$One <- strftime(data$One, format="%M:%S", tz="GMT")
data$Two <- strftime(data$Two, format="%M:%S", tz="GMT")
data$Three  <- strftime(data$Three, format="%M:%S", tz="GMT")
data$Four <- strftime(data$Four, format="%M:%S", tz="GMT")
data$Five <- strftime(data$Five, format="%M:%S", tz="GMT")
print(xtable(data), type = "html",include.rownames=FALSE)
```


## Information

<a href="Drakes.pdf" target="_blank" class="btn btn-lg btn-outline">
    <i class="fa fa-file-pdf-o"></i>
    Download file
</a>

## Timeline

- Load Bus on East Campus between football and baseball fields: 1:10pm EDT
- Depart for Bowling Grren, KY: 1:20pm EDT
- Rest Room Break
- Arrive at Phil Moore Park: 4:20pm EDT
- Women's 5k: 5:45pm EDT
- Men's 8k: 6:30pm EDT

NOTE: The meet s in the CENTRAL Time Zone. All times listed here are EASTERN. 

## Maps

Men

<iframe id='mapmyfitness_route' src='https://www.mapmyrun.com/routes/view/embedded/4638244486?width=600&height=400&&line_color=E68006c6&rgbhex=c60680&distance_markers=1&unit_type=imperial&map_mode=SATELLITE&show_marker_every=1&last_updated=2021-09-16T19:38:52+00:00' height='400px' width='100%' frameborder='0'></iframe><div style="padding-left:8px;padding-top:8px;padding-bottom:8px"><a target="_blank" rel="noopener noreferrer" href="https://www.mapmyrun.com/routes/view/4638244486">More Details</a></div>


Women

<iframe id='mapmyfitness_route' src='https://www.mapmyrun.com/routes/view/embedded/4638255613?width=600&height=400&&line_color=E68006c6&rgbhex=c60680&distance_markers=0&unit_type=imperial&map_mode=SATELLITE&show_marker_every=1&last_updated=2021-09-16T19:47:20+00:00' height='400px' width='100%' frameborder='0'></iframe><div style="padding-left:8px;padding-top:8px;padding-bottom:8px"><a target="_blank" rel="noopener noreferrer" href="https://www.mapmyrun.com/routes/view/4638255613">More Details</a></div>
