---
title: "Georgetown College XCTF 2021-2022"
author: "Luke Garnett"
date: "Updated:`r Sys.time()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth:  4
    css: style.css
---


```{r include=FALSE}
require(knitr)
require(mosaic)
require(DT)
require(kableExtra)
library(xtable)
library(readxl)
library(rJava)
library(xlsx)
library(googlesheets4)
```

# 2021-2022 Information {.tabset}

## XC Calendar {.tabset}

Meal Schedule for Aug 14th-Aug 20th:

- Breakfast: 8am-9am, Student Center / Grill
- Lunch: 11:30am-1:30pm, East Campus Conference Center
- Lunch: 5:30pm-7:30pm, East Campus Conference Center

We may end up having more specific meal times so that teams are staggered. These times and locations are subject to change. 

Select a month or group below:

### August


```{r echo=FALSE, results='asis'}

data <- read.xlsx2("Schedule.xlsx",sheetIndex=1,
                  colClasses=c("Date","character","character","character"))
tf <- read.xlsx2("Schedule.xlsx",sheetIndex=2,
                  colClasses=c("Date","character","character","character"))

aug <- data[data$Date<as.Date("2021-09-01"),]
aug[,1]=as.character(aug[,1])
print(xtable(aug),type='html',include.rownames=FALSE)
```

### September

```{r echo=FALSE, results='asis'}

sept <- data[data$Date<as.Date("2021-10-01") & data$Date>as.Date("2021-08-31"),]
sept[,1]=as.character(sept[,1])
print(xtable(sept),type='html',include.rownames=FALSE,sanitize.text.function = function(x){x})
```

### October

```{r echo=FALSE, results='asis'}

oct <- data[data$Date<as.Date("2021-11-01") & data$Date>as.Date("2021-09-30"),]
oct[,1]=as.character(oct[,1])
print(xtable(oct),type='html',include.rownames=FALSE,sanitize.text.function = function(x){x})
```

### November

```{r echo=FALSE, results='asis'}

nov <- data[data$Date<as.Date("2021-12-01") & data$Date>as.Date("2021-10-31"),]
nov[,1]=as.character(nov[,1])
print(xtable(nov),type='html',include.rownames=FALSE,sanitize.text.function = function(x){x})
```

### Meets

```{r echo=FALSE, results='asis'}

meets <- data[data$Type=="Meet",]
meets[,1]=as.character(meets[,1])
print(xtable(meets),type='html',include.rownames=FALSE,sanitize.text.function = function(x){x})
```

## Freshmen Info

Freshmen: two major things need to be completed by August 1st

### PlayNAIA

All freshmen are required to register with the NAIA Eligibility Center at the following link: <a href="https://play.mynaia.org/">PlayNAIA</a>

The NAIA charges a 1 time fee around $100 that GC is not allowed to cover and you will be required to send in transcripts. PLEASE GET YOUR END OF THIS TAKEN CARE OF BEFORE AUGUST 1st!!!!! Once you have sent in the required documents it can take a few weeks for the NAIA to review and clear you to compete. So this needs to be done ASAP!

Once you register, you will be assigned an NAIA-ID number. Please let me know what that number.

### Insurance Information and Physicals

Stacee Gibson from Athletic Training should have sent you Insurance form information to you Georgetown College Email. PLEASE GET THIS DONE BEFORE AUGUST 1st!

If you have any issues with the forms, please email Stacee at: stacee_gibson@georgetowncollege.edu

Physicals will be FREE and they must be performed by a doctors that GC's insurance has approved in order for you to be covered by GC insurance. (We are partnered with UK Healthcare, so you will be seen by UK Healthcare doctors) Your physical cannot be completed unless you have filled out the forms!


## TF Calendar


```{r echo=FALSE, results='asis'}

aug <- tf[tf$Date<as.Date("2021-09-01"),]
aug[,1]=as.character(aug[,1])
print(xtable(aug),type='html',include.rownames=FALSE)
```

## Testing



<a href="meetInfo2021.html">Testing</a>


