---
title: "Weekly Training Plan"
author: "Georgetown College Cross Country"
date: "Week Of: 7/5/2020 - 7/11/2020"
output:
  html_document:
    toc: TRUE
    toc_float: TRUE
    css: style.css
  pdf_document: default
---


```{r include=FALSE}
require(knitr)
require(mosaic)
require(DT)
require(kableExtra)
library(xtable)


data = read.csv("training.csv",header=TRUE)
workout1 = read.csv("workout3.csv",header=TRUE)
workout2 = read.csv("workout1.csv",header=TRUE)
men = data[data$Sex=='M',]
men = men[order(men$Name),]
women = data[data$Sex=='F',]
women = women[order(women$Name),]

createTable=function(trainPlan){
  
  Day=c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")
  Type=trainPlan[seq(4,24,3)]
  Paces=trainPlan[seq(6,24,3)]
  Miles=trainPlan[seq(5,24,3)]
  

  table=data.frame(Day, Type, Paces, Miles) 
  names(table)=c("Day","Run Type", "Pace(s)", "Total Miles")
  return(table)
}

strengthTable = function(workout){

cat("<table border='1'>")
  cat("<tr>")
    cat("<th>Reps</th>")
    cat("<th class='threefourths'>Exercise</th>")
  cat("</tr>")

  length=length(workout[,2])
  for(i in 1:length){
    link =paste("<a href='", workout[i,3]  ,"'  target='_blank'>",workout[i,2]  ,"</a>")
    cat("<tr>")
      cat("<td>")
        cat(as.character(workout[i,1]))
      cat("</td>")
      cat("<td class='threefourths'>")
        cat(link)
      cat("</td>")
    cat("</tr>")
    
  }
  


  
cat("</table>")

  cat("\n")
  cat("\n")
}

```

## Notes


## Strength Workouts


### Tuesday

500 Abs!

### Saturday

500 Abs!

## Stretching Routine 

- Pre run stretching routine (DYNAMIC.)
  - Arm circles: 5 each direction, each arm (20 total)
  - Leg swings, side to side: 10 each leg
  - Leg swings, front to back: 10 each leg
  - Walking lunges: 5 each
  - High knees: 10 each 
  - Butt kicks: 10 each
  - Grapevines/Karaoke: 5 each
  - Any other DYANMIC stretch you need
  
- Post run stretching (STATIC)
  - Toe touch: 15 sec
  - Cross leg toe touch: 15 sec each
  - Calf stretch: 15 sec each
  - Quad stretch: 15 sec each
  - Shoulder Stretch: 15 sec each
  - Butterfly: 15 sec
  - Foam Roll (If you want)
  - Any other stretch you need
  

## Men

```{r echo=FALSE, results='asis'}

length=length(men[,1])

for(i in 1:length){
  
  final=createTable(t(men)[,i])
  
  cat("###", as.character(men[i,1]), "\n")
  cat("\n")
  cat("Your mileage for this week is", men[i,25], "miles.")
  cat("\n")
  cat("\n")

  cat('<div class="column">')
  cat('<div class="row">')
  
  print(xtable(final), type = "html",include.rownames=FALSE)
  
  cat('</div>')
  
  cat('<div class="row">')
  
  
  cat('</div>')
  cat('</div>')
 
  cat("\n")
  cat("Your planned mileage for next week will be", men[i,26], "miles.")
  cat("\n")
  cat("\n")
}

```




## Women

```{r echo=FALSE, results='asis'}



length=length(women[,1])

for(i in 1:length){
  
  final=createTable(t(women)[,i])
  
  cat("###", as.character(women[i,1]), "\n")
  cat("\n")
  cat("Your mileage for this week is", women[i,25], "miles.")
  cat("\n")
  cat("\n")
  
  cat('<div class="column">')
  cat('<div class="row">')
  
  print(xtable(final), type = "html",include.rownames=FALSE)
  
  cat('</div>')

  cat('<div class="row">')
  

  cat('</div>')
  cat('</div>')
  
  cat("\n")
  cat("Your mileage for next week will be", women[i,26], "miles.")
  cat("\n")
  cat("\n")

}

```




